Honey Bee Colonies Impacted by Varroa, American Foulbrood and Global Warming

### 2024-08-02 starter-analysis-exercise/products/report/manuscript_final-2.qmd
Update to Flow Chart Removed snippit 08.02.24
updated workflow schematic 08.02.24

#knitr::include_graphics(here("assets","antigen-recognition.png"))
```

>>>>

```{r}
# Install necessary packages
if (!require("DiagrammeR")) install.packages("DiagrammeR")

# Load the DiagrammeR package
library(DiagrammeR)

# Create the flowchart using DiagrammeR
grViz("
  digraph Data_Analysis_Flowchart {
    graph [layout = dot, rankdir = LR, label = 'Workflow Schematic', fontsize = 45, labelloc = 't']

    node [style = filled, fontsize = 20, width = 2, height = 2]

    Define_Objectives [label = 'Define Objectives', shape = oval, color = lightblue]
    Collect_Data [label = 'Collect Data', shape = box, color = lightgreen]
    Clean_Data [label = 'Clean Data', shape = ellipse, color = lightyellow]
    Analyze_Data [label = 'Analyze Data', shape = diamond, color = lightcoral]
    Interpret_Results [label = 'Interpret Results', shape = trapezium, color = lightgrey]
    Visualize_Data [label = 'Visualize Data', shape = parallelogram, color = lightpink]
    Compile_Report [label = 'Compile Report', shape = house, color = lightcyan]
    Review_Revise [label = 'Review & Revise', shape = invhouse, color = lightgoldenrodyellow]
    Present_Report [label = 'Present Report', shape = hexagon, color = lightseagreen]

    Define_Objectives -> Collect_Data
    Collect_Data -> Clean_Data
    Clean_Data -> Analyze_Data
    Analyze_Data -> Interpret_Results
    Interpret_Results -> Visualize_Data
    Visualize_Data -> Compile_Report
    Compile_Report -> Review_Revise
    Review_Revise -> Present_Report
  }
")
